\section*{References}

\begin{thebibliography}{1}

%Intro: 
\bibitem{cmscomptdr} Bonacorsi D {\it et al.} 2007 The CMS computing model 
{\it Nucl. Phys.} B {\it (Proc. Suppl.)} {\bf 172} 53-56

\bibitem{scalability}
 Belforte S {\it et al.} 2010 Bringing the CMS distributed computing system into scalable operations 
{\it J. Phys.: Conf. Ser.} {\bf 219} 062015

\bibitem{spacemon}
N Ratnikova {\it et al.} 2014 CMS Space Monitoring {\it J. Phys.: Conf. Ser.} {\bf 513} 042036 

\bibitem{PhEDEx}
  Egeland R, Wildish T and Metson S 2008 Data transfer infrastructure for CMS data taking,  
{\it XII Advanced Computing and Analysis Techniques in Physics Research (Erice, Italy: Proceedings of Science)}


% central infrastructure section: 
% Tony's references for SiteDB and Data Service 

\bibitem{SiteDB} 
Metson S {\it et al.} 2010 SiteDB: marshalling people and resources available to CMS
{\it J. Phys.: Conf. Ser.} {\bf 219} 072044

% For DMWMMON DB and data-service, you can refer to them as based on the PhEDEx data-service:

\bibitem{DataService} 
 R Egeland {\it et al.} 2010  PhEDEx Data Service 
{\it J. Phys.: Conf. Ser.} {\bf 219} 062010

% References for visualization from Eddie: 
\bibitem{ExpDashboard} 
  Andreeva J {\it et al.} 2012 Experiment Dashboard - a generic, scalable solution for 
monitoring of the LHC computing activities, distributed sites and services 
{\it J. Phys. Conf. Ser.} {\bf 396} 032093

\bibitem{DDMAccounting} 

Karavakis E {\it et al.}  2014 Common Accounting System for Monitoring the ATLAS 
Distributed Computing Resources
{\it J. Phys.: Conf. Ser.} {\bf 513} 062024

\bibitem{storagedumps}
Huang C-H {\it et al.} 2012 Data Storage Accounting and Verification at LHC experiments 
{\it J. Phys.: Conf. Ser.} {\bf 396} 032090

\bibitem{cmsdatamanagement}
M Giffels {\it et al.} 2014 The CMS Data Management System {\it J. Phys.: Conf. Ser.} {\bf 513} 042052

%references from CHEP2012 paper:
\bibitem{wlcg} Knobloch J {\it et al.} 2005 "LHC Computing Grid Technical Design Report" CERN-LHCC-2005-024
\bibitem{ATLASDDM} Garonne V, Molfetas A, Lassnig M, Barisits M, Stewart G A, Beermann T 2012 "The ATLAS Distributed Data Management project: Past and Future", these proceedings
\bibitem{SRM} Shoshani A,  Sim A and  Gu J 2002 ``Storage Resource Managers: Middleware Components for Grid Storage'',  Nineteenth IEEE Symposium on Mass Storage Systems'
\bibitem{cms} The CMS Collaboration 2008 "The CMS experiment at the CERN LHC" JINST {\bf 3} S08004
\bibitem{DBS3} Giffels M and Guo Y Data Bookkeeping Service 3 - A new event data catalog for CMS, submitted to CHEP 2012
\bibitem{phedex} Egeland R, Wildish T and Metson S 2008 "Data transfer infrastructure for CMS data taking" {\it XII Advanced Computing and Analysis Techniques in Physics Research} (Erice, Italy: Proceedings of Science)
\bibitem{filelight} Ball G 2011 PhD thesis, chapter 8 ``Computing Monitoring Pages",
 https://workspace.imperial.ac.uk/highenergyphysics/Public/theses/Ball.pdf
\bibitem{d3} The D3 javascript library http://mbostock.github.com/d3/
\bibitem{LHCbDiracFramework} Stagni F {\it et al.} 2012: "LHCbDIRAC: distributed computing in LHCb",  these proceedings 
\bibitem{SLS} Lopienski S 2008 ``Service level status - a new real-time status display for IT services'' {\it J. Phys.: Conf. Ser.}  {\bf 119} 052025
%\bibitem{SRMspecs}  Sim A and Shoshani A 2009 The Storage Resource Manager Interface Specification Version 2.2,  https://sdm.lbl.gov/srm-wg/doc/SRM.v2.2.html


%\bibitem{LFCandDPM}  "Official Documentation for LFC and DPM"  https://twiki.cern.ch/twiki/bin/view/LCG/DataManagementDocumentation  
\bibitem{LFC} Baud J-Ph et al 2005 Performance analysis of a file catalog for the LHC computing grid HPDC
14 91-99
\bibitem{LHCbDiracBookkeeping} Charpentier P  {\it et al.} 2012 "The LHCb Data Management System",  these proceedings 
\bibitem{Serfon:2010zz} 
  Serfon C 2010
  "Data management tools and operational procedures in ATLAS: Example of the German cloud,"
  J.\ Phys.\ Conf.\ Ser.\  {\bf 219}, 042053 (2010).
  %%CITATION = 00462,219,042053;%%
\bibitem{Magini:2011zz} 
  N.~Magini, N.~Ratnikova, P.~Rossman, A.~Sanchez-Hernandez and T.~Wildish,
  "Distributed data transfers in CMS,"
  J.\ Phys.\ Conf.\ Ser.\  {\bf 331}, 042036 (2011).
  %%CITATION = 00462,331,042036;%%
\bibitem{ElisaTwiki} Lanciotti E 2011 "Storage elements dumps and consistency checks versus file catalogues"
https://twiki.cern.ch/twiki/bin/view/LCG/ConsistencyChecksSEsDumps
\bibitem{Sciaba:chep2012}Bauerdick L and Sciaba A 2012 "Towards a global monitoring system for CMS computing", these proceedings
\bibitem{syncat} Millar P {\it et al.} 2010 ``Dealing with orphans: Catalogue synchronisation with SynCat'' J. Phys.: Conf. Ser. 219 062060
\bibitem{namespace} Sanchez-Hernandez A, Egeland R, Huang C-H, Ratnikova N, Magini N and Wildish T, 2012 "From toolkit to framework - the past and future evolution of PhEDEx", these proceedings
\bibitem{castor} Castor, http://castor.web.cern.ch/castor/
\bibitem{dcache} dCache,  http://www.dcache.org/
\bibitem{dpm} DPM (Disk Pool Manager) https://twiki.cern.ch/twiki/bin/view/LCG/DataManagementDocumentation\#DPM
\bibitem{eos} Peters A-J  2011 ``The EOS disk storage system at CERN'',  ACAT conference proceedings
\bibitem{bestman} BeStMan ( Berkeley Storage Manager) https://sdm.lbl.gov/bestman/
\bibitem{lustre} Lustre http://www.lustre.org/ 
\bibitem{lstore} L-Store (Logistical Storage)  http://www.accre.vanderbilt.edu/mission/services/lstore.php
%\bibitem{storm} StoRM (Storage Resource Manager),  http://storm.forge.cnaf.infn.it/
\bibitem{storm-gpfs}  Cavalli A  {\it et al} 2010  ``StoRM-GPFS-TSM: A new approach to hierarchical storage management for the LHC experiments''  {\it J. Phys.: Conf. Ser.} {\bf 219} 072030
\bibitem{xrootd} XRootD,  http://xrootd.slac.stanford.edu/
\bibitem{protovis} The Protovis javascript library http://mbostock.github.com/protovis/
\bibitem{highcharts} The Highcharts javascript library http://www.highcharts.com/

\bibitem{matplotlib} Matplotlib python 2D plotting library http://matplotlib.sourceforge.net/


\end{thebibliography}

% References from the poster: 

%1.http://iopscience.iop.org/1742-6596/396/3/032090/pdf/jpconf12_396_032090.pdf 
%2.https://github.com/dmwm/DMWMMON/tree/master/SiteInfoProviders
%3. https://twiki.cern.ch/twiki/bin/view/CMSPublic/SpaceMonSiteAdmin 
%4.http://dashb-ssb.cern.ch/dashboard/request.py/siteview#currentView=test
%5. http://dashb-atlas-ddm-acc.cern.ch/dashboard/request.py/ddmaccounting 
%6.http://rucio-hadoop.cern.ch/rucio/accounting/

